Mentored data science research with tweets

### 2020-04-18 Rmd/jse-2019-ms.Rmd
ignored lit folder; added to todo list

@@

>>>>

The content of tweets over time particularly intrigued us. We 
hypothesized that high-profile social media events would generate lots of tweets, and that we'd detect social media events through changes in tweet topic content over time.

@@

### Collecting tweets

We collected tweets by automated, repeated querying of Twitter's 
streaming API. This involved multiple steps. First, we created a 
new account on Twitter. With these user credentials, we used the 
R package `rtweet` to query the API. Because we work on computers 
with linux operating systems, we made use of linux software 
`crontab` to repeatedly execute R code to submit API queries. Each 
query lasts a user-specified duration. We timed the API queries so 
that there was no time lag between queries. We stored API query 
results in their native JSON format. The R package `rtweet` 
provides functions that parse tweet JSON to R data frames. We then 
conducted all further analyses with the R data frames.
